Speculation in foreign exchange: noise or information

### 2015-09-09 Knitr/NewPaper.Rnw
Extreme.R now has the comparison of extreme and regular distribution This needs to be turned into a function that produces graphs and table.

\documentclass[12pt, a4paper, oneside]{article} % Paper size, default font size and one-sided paper
%\graphicspath{{./Figures/}} % Specifies the directory where pictures are stored
%\usepackage[dcucite]{harvard}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pdflscape}
\usepackage{appendix}
\usepackage[flushleft]{threeparttable}
\usepackage{multirow}
\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
\usepackage{graphicx}
%\bibliographystyle{plainnat}
\bibliographystyle{agsm}
\usepackage[colorlinks = true, citecolor = blue, linkcolor = blue]{hyperref}
%\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - change to black if annoying
%\renewcommand[\harvardurl]{URL: \url}
 \usepackage{listings}
  \usepackage{tikz}
 \usetikzlibrary{arrows,positioning}
 \usepackage{color}
 %\graphicspath{{../Pictures/}}
\definecolor{mygrey}{gray}{0.95}
\lstset{backgroundcolor=\color{mygrey}}
\begin{document}
\title{Speculation in foreign exchange: noise or information}
\author{Rob Hayward\footnote{University of Brighton Business School, Lewes Road, Brighton, BN2 4AT; Telephone 01273 642586.  rh49@brighton.ac.uk. }} 
\date{\today}
\maketitle
\begin{abstract}
  If speculation is just noise, price movements associated with extremes of speuclative sentiment or heavy involvement of speculative activity should be reveversed; if speculation is informed, associated price movement is more likely to be sustained.  A unique set of risk-reversals on currency options is used to measure speculative sentiment and regulatory positions measure speculative activity. An event study shows that extremes do not increase the probability of a price reversal, supoprting the view that speculation is part of the price disovery process.     
\end{abstract}
\section*{Introduction}
Ideas about the way that speculation affects financial market span a broad range.  Towards one end is the Keynesian view that speculation is a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd'' \citet[p. 101]{Keynes1936}. Speculation is a problem that will cause booms, reversals and will discourage fundamental, long-term investment; It is noise that emerges from the interaction of collective sentiment to encourages trends in asset prices.

@@

This paper contributes to the debate about the nature of speculation in a number of ways. A unique set of option prices are used to identify the intensity of speculative sentiment; an event study method is used to establish the effect of extremes of speulative sentiment and speculative positions; these speculative extremes are compared to a common noise-trader model.  Speculative extrmes do not provide information about the future; the evolution of foreign exchange prices after an extreme can be chracterised as a random walk; this suggests that speculation is part of the process of price discovery.

For example, Figure \ref{fig:ES1} show the evolution of a selection of foreign exchange prices after an exrtreme reading of speculative sentiment. Sentiment is measured by an extreme in the price of currency call options relative to the equivalent put.  It is clear that the foreign exchange rate has a contemporaneous movement with the sentiment but that after reading the extreme, there is no clear direction.  The lack of clear direction indicates lack of information.  As such, extreme speuclative positions do presage reversales, indicating that they are not associated with divergence from equilibrium.

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.6]{RRCum16}
\caption{Event Study:  Extreme (High 99th percentile) Risk Reversal Skew and 16 day event window: Risk reversals are the ratio of implied volatility on calls to the equivalent put; extreme high is the hghest 99th percentile for the whole range, cumulative returns are the sum of log exchange rate returns.  The event day is the day of the extreme risk reversal reading as a proxy for extreme speculative sentiment.  If speculation is uninformed, extremes shoudl be followed by reversals; if specuation is informed, extremes are more likely to be followed by a random walk.}
\label{fig:ES1}
\end{figure}
% This description provides an explanation for the observation from \citet{ShillerVol} that stock prices are more volatile than the underlying earnings information on which valuation should be based. In addition, \citet{Delong1990noise} and \citet{shleifer1997limits} show that constrained horizons can cause noise-trading to limit the ability of informed traders to take advantage of profitable opportunities for fear of further divergence from fundamental value before realignment is achieved.

The nature of speculation is central to many contemporary questions about international financial markets. For example, regulations or taxes that reduce the amount of speculation may be beneficial if they limit risk-taking and encourage more long-term attitudes towards investment.  If speculation is largely uninformed it will add to the level of noise and maker it even harder for informed-traders to overcome uncertainty and apply fundamental information about long-term value. It will increase the tendency towards activity that is focused on the short-term.  However, if speculation is informed and part of the process of price discovery, regulatory measures may reduce liquidity and undermine the pricess of price discovery. Increased volatilty, heightened risk and reduced transparency together with other costs may provide an countervailing force.

The rest of the paper proceeds as follows:  Section Two analyses the distinction between informed and uninformed speuclators; Section Three discusses the measurement of speculation and the testing of extreme positions; Section Four reviews the evidence; Section Five concludes with a discussion of policy implications.

\section{Informed and uninformed traders}
Speculation plays an  important role in the areas of market-microstructure, the rationale for the trading of financial securities and rational expectations. However, there is no clear, unambiguous theory of speculation.  While speculation may be viwed as being informed or uninformed, those trading without information are often categorised as being either \emph{noise-traders} or \emph{liquidity traders}.

Noise-trading is associated with psychogical biases and restricted information while liquidity-trading is about institutional constraints.  Therefore, noise is associated with behavioural issues, over-confidence and the use of irrational or purely fashionable investment tools. See \citet{DeBondtAnalysts} for an analysis of over-reaction and the \emph{represetntativeness heuristic}, \citet{OdeanOC} for a study of over-confidence and  \citet{ShillerFashion} for an assessment of investment fads.  Market-participants do not make decisions independently of those made by others. Information is inferred from the activities of others. \citet[p.101]{Keynes1936} said investment decisions could be based on the expecttions of others' valuations.  institutional constraints may mean that economic agents just execute customer orders at the current price or it may be that they buy and sell with reference to a benchmark index or to fulfil a hedging strategy. The institutional explanations are associated with the allocation of credit for investment and trading purposes:  as asset values decline exchanges, banks and other providers of liquidity require larger margins and deeper haircuts; investors liquidate their fund holdings; the attraction of hedging increases.  See \citet{BrunnermeierLiquidity} and \citet{Gorton} for some discussion of the way that margin-calls and collaeral constraints can force investment decisions.  However, the terms are not fixed and  \citet[p. 1]{GortonNoise} categorise noise-traders as all those trading in markets for ``non-information-based reasons''.

@@

\citet{EasleyPIN} use informaton as an explanation for the effect of large orders on stock prices.  The \emph{order effect} may be a consequence of the need to adjust inventories when a market-maker recieves a large order; it may also be a function of the market-maker knowledge that large orders are more likely to informed traders seeking to take advantage of their informational advantage.  \citet{EasleyPIN2} develop a technique to estimate the probability that trading is informed.  The find that the high liquidity stocks have the highest level of information and the most frequent arrival rate of informed traders but that this is more than offset by the high quantity of uninformed traders.  Low liquidity stock, by contrast, have fewer information events but informed traders have a much larger effect on prices.

Informed speculation is also used as the theoetical justification for the tendency of Rational Expectations Equilibrium (REE) to prevail in the long-run.  Those economic agents able to determine the fundamental value or discern the underlying economic model will be able to speculate or sell forecasts that will tend to drive prices towards the equilibrium \citet{muth1961Rational}.  This tends to leave uninformed speculation as a pure noise that can be characterlised as white-noise random variable. While this construction may be justified for the analysis of microstructure and market efficiency, it is an over-simplification that is inappropriate when seeking more understanding of speculation itself.  Institutional and psychological explanations for noise-trading frequently suggest that there are endogenous non-random elements to speculative activity.

However, a large proportion of uninformed traders in the market can undermine this process.  \citet{Delong1990noise} and \citet{shleifer1997limits} have presented models where \emph{noise-trader risk} can prevent the arbitrate of informed speculators from driving prices back towards the fundamental value.  The risk that noise-traders will drive prices even further away from equilibrium before the convegence can limit the activity of informed speculators when they are risk averse.\footnote{This three-period, overlapping generation model with informed and uininformed traders has a price equation \begin{equation}
p_t = 1 + \frac{\mu(\rho_t - \rho^*)}{1 + r} + \frac{ \mu \rho^*}{r} - \frac{2 \gamma \mu^2 \sigma_{\rho}^2}{r(1 + r^2)}.
\label{eq:NP2}
\end{equation} 
 where $p_t$ is the price; $\mu$ is the share of uninformed traders; $\rho$ is the price mis-perception of the uninformed traders; $\gamma$ is the level of risk aversion; $\sigma^2_{p,t+1}$ is the variance of the misperception.}

@@

The Friedman-effect is the activity of informed speulators.  They take advantage of the space that has been created by the price pressure of the uninformed traders to profit from this mis-pricing.  Uniformed traders tend to hold more when their opinions are strong.  This is the noise-trader risk that can prevent informed traders from fulfuillig their arbitrage role. If uninformed traders are very prominent or have strong opinions, prices should show the greatest divergence from fundamental value and the risk of a reversal shoould be at its greatest.

\subsection{Empirical work}
Empirical assessment of speculation has been limited by the scarcity of data.  It is not very easy to distinguish between speculators and other types of investors.  It is even harder to distinguish between the informed and uninformed.  One approach has been to assume that noise-traders utilise simple investment strategies and to use tests of these strategies as a means of testing speculation.  Common strategies that have been used are momentum (ref), contrarian (ref) and carry (ref).   It is also possible to assume that certain investors usually have more information than others.  For example, hedge funds, investment banks and other professionals can be assuemd to be informed while retail or day traders may be uninformed.

@@

However, identifying large orders and making an assessment of the level of informed trading based on that is much harder to achieve in an over-the-counter market like foreign exchange. While electronic order books have become more widely used in recent years, much of the activity still takes place through bilateral agreements.  Information about the nature of transactions including size and origin of orders is not widely available\footnote{\citet{Lyons1995Microstructure} and \citet{Evans2002Order} have used the initiation of orders as an explanatory variable in an equation to explain the evolution of major exchange rates.  They find that $\$$ 1 billion of net US dollar purchase moves the deutsche mark price of the US unit by 0.5 percent. They argue that the orders cystalise a range of information that is used to value currencies.}    \citet{LeeandReady} seek to use price action to infer the nature of the order that has been placed into the market.  Their tick test has four classifications: the uptic, the downtick, the zero-uptick and the zero-downtick. A trade is an uptick if the price is higher than the previous trade.  If the price is the same as the previous trade, if the previous trade was classified as an uptick, this trade is a zero-uptick.  
\section{Methodology}
The aim of this study is to assess whether speculation in the foreign exchange market is informed or uninformed. Speculation must be identified and then extreme speculation will then be compared with what would be expected if it were informed or uninformed.  If informed and part of the price-discovery process, extreme speculation would be a function of perceived divergence from equilibrium or new information.  The following price performance should be a random walk.  If speculation is uninformed, extremes should cause a divergence from fundamental value and a price reversal should be anticiapted.

@@

\section{Speculation and foreign exchange returns}
This paper has sought to measure speculation and to use this measure to discover more about the relationship between speculation, information and asset prices.  
Whether measured as intensity of speculative sentiment or as the weight of speculator action, it is clear that extreme speculation does not provide information about future returns.  This means that specualtion is more likely to be informed than uninformed.  If it were uninformed it woudl be much more likely that these extremes would be followe by reversals as informed market participants took advantage of the space created by this uninformed speculative activity.

@@

The nature speculation is central to a number of contemporary policy questions.  Amongst these are the design and regulation of financial markets, the surge in commodity prices and the kimits put on the activities of financial institutions. The debate about a tax on financial transactions, initiated by \citet{TobinTax} and now called the \emph{the Tobin tax}, has been intended to reduce speculation. The argument for a tax on financial transactions depends on the idea that speculators will drive the price away from its fundamental value. However, if speuclation is part of the process of price discovery, reducing its activity may incure costs that offset some of the benefits that are expected.

The reduction in speculation in the US government bond market that has been seen since the introduction of new costs and restrictions under the array of ???? regulations has been seen by some to reduce liquidity and increase volatiolity, rising risk and imposing additional costs for final investors.

>>>>

\documentclass[12pt, a4paper, oneside]{article} % Paper size, default font size and one-sided paper
%\graphicspath{{./Figures/}} % Specifies the directory where pictures are stored
%\usepackage[dcucite]{harvard}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{pdflscape}
\usepackage{appendix}
\usepackage[flushleft]{threeparttable}
\usepackage{multirow}
\usepackage[comma, sort&compress]{natbib}% Use the natbib reference package - read up on this to edit the reference style; if you want text (e.g. Smith et al., 2012) for the in-text references (instead of numbers), remove 'numbers' 
\usepackage{graphicx}
%\bibliographystyle{plainnat}
\bibliographystyle{agsm}
\usepackage[colorlinks = true, citecolor = blue, linkcolor = blue]{hyperref}
%\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - change to black if annoying
%\renewcommand[\harvardurl]{URL: \url}
 \usepackage{listings}
  \usepackage{tikz}
 \usetikzlibrary{arrows,positioning}
 \usepackage{color}
 %\graphicspath{{../Pictures/}}
\definecolor{mygrey}{gray}{0.95}
\lstset{backgroundcolor=\color{mygrey}}
\begin{document}
\title{Speculation in foreign exchange: noise or information}
\author{Rob Hayward\footnote{University of Brighton Business School, Lewes Road, Brighton, BN2 4AT; Telephone 01273 642586.  rh49@brighton.ac.uk. }} 
\date{\today}
\maketitle
\begin{abstract}
 Uninformed speculation based on noise should lead to price reversals; informed speculation is sustainable. A unique set of option prices measure speculative sentiment while regulatory positions determine the weight of speculative activity.  An event study shows that extremes of speculative sentiment or speculative activity do not increase the probability of price reversal.  Price activity after the extreme is close to a random walk. This supports the view that speculation is part of the price-discovery process.      
\end{abstract}
\section*{Introduction}
Ideas about the way that speculation affects financial market span a broad range.  Towards one end is the Keynesian view that speculation is a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd'' \citet[p. 101]{Keynes1936}. Speculation is a problem that will cause booms, reversals and will discourage fundamental, long-term investment; It is noise that emerges from the interaction of collective sentiment to encourages trends in asset prices.

@@

This paper contributes to the debate about the nature of speculation in a number of ways. A unique set of option prices are used to identify the intensity of speculative sentiment; an event study method is used to establish the effect of extremes of speculative sentiment and speculative positions; these speculative extremes are compared to a common noise-trader model.  Speculative extremes do not provide information about the future; the evolution of foreign exchange prices after an extreme can be characterised as a random walk; this suggests that speculation is part of the process of price discovery.

For example, Figure \ref{fig:ES1} show the evolution of a selection of foreign exchange prices after an extreme reading of speculative sentiment. Sentiment is measured by an extreme in the price of currency call options relative to the equivalent put.  It is clear that the foreign exchange rate has a contemporaneous movement with the sentiment but that after reading the extreme, there is no clear direction.  The lack of clear direction indicates lack of information.  As such, extreme speculative positions do presage reversals, indicating that they are not associated with divergence from equilibrium.

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.6]{RRCum16}
\caption{Event Study:  Extreme (High 99th percentile) Risk Reversal Skew and 16 day event window: Risk reversals are the ratio of implied volatility on calls to the equivalent put; extreme high is the highest 99th percentile for the whole range, cumulative returns are the sum of log exchange rate returns.  The event day is the day of the extreme risk reversal reading as a proxy for extreme speculative sentiment.  If speculation is uninformed, extremes should be followed by reversals; if speculation is informed, extremes are more likely to be followed by a random walk.}
\label{fig:ES1}
\end{figure}
% This description provides an explanation for the observation from \citet{ShillerVol} that stock prices are more volatile than the underlying earnings information on which valuation should be based. In addition, \citet{Delong1990noise} and \citet{shleifer1997limits} show that constrained horizons can cause noise-trading to limit the ability of informed traders to take advantage of profitable opportunities for fear of further divergence from fundamental value before realignment is achieved.

The nature of speculation is central to many contemporary questions about international financial markets. For example, regulations or taxes that reduce the amount of speculation may be beneficial if they limit risk-taking and encourage more long-term attitudes towards investment.  If speculation is largely uninformed it will add to the level of noise and maker it even harder for informed-traders to overcome uncertainty and apply fundamental information about long-term value. It will increase the tendency towards activity that is focused on the short-term.  However, if speculation is informed and part of the process of price discovery, regulatory measures may reduce liquidity and undermine the prices of price discovery. Increased volatility, heightened risk and reduced transparency together with other costs may provide an countervailing force.

The rest of the paper proceeds as follows:  Section Two analyses the distinction between informed and uninformed speculators; Section Three discusses the measurement of speculation and the testing of extreme positions; Section Four reviews the evidence; Section Five concludes with a discussion of policy implications.

\section{Informed and uninformed traders}
Speculation plays an  important role in the areas of market-microstructure, the rationale for the trading of financial securities and rational expectations. However, there is no clear, unambiguous theory of speculation.  While speculation may be vowed as being informed or uninformed, those trading without information are often categorised as being either \emph{noise-traders} or \emph{liquidity traders}.

Noise-trading is associated with psychological biases and restricted information while liquidity-trading is about institutional constraints.  Therefore, noise is associated with behavioural issues, over-confidence and the use of irrational or purely fashionable investment tools. See \citet{DeBondtAnalysts} for an analysis of over-reaction and the \emph{representativeness heuristic}, \citet{OdeanOC} for a study of over-confidence and  \citet{ShillerFashion} for an assessment of investment fads.  Market-participants do not make decisions independently of those made by others. Information is inferred from the activities of others. \citet[p.101]{Keynes1936} said investment decisions could be based on the expectations of others' valuations.  institutional constraints may mean that economic agents just execute customer orders at the current price or it may be that they buy and sell with reference to a benchmark index or to fulfil a hedging strategy. The institutional explanations are associated with the allocation of credit for investment and trading purposes:  as asset values decline exchanges, banks and other providers of liquidity require larger margins and deeper haircuts; investors liquidate their fund holdings; the attraction of hedging increases.  See \citet{BrunnermeierLiquidity} and \citet{Gorton} for some discussion of the way that margin-calls and collateral constraints can force investment decisions.  However, the terms are not fixed and  \citet[p. 1]{GortonNoise} categorise noise-traders as all those trading in markets for ``non-information-based reasons''.

@@

\citet{EasleyPIN} use information as an explanation for the effect of large orders on stock prices.  The \emph{order effect} may be a consequence of the need to adjust inventories when a market-maker receives a large order; it may also be a function of the market-maker knowledge that large orders are more likely to informed traders seeking to take advantage of their informational advantage.  \citet{EasleyPIN2} develop a technique to estimate the probability that trading is informed.  The find that the high liquidity stocks have the highest level of information and the most frequent arrival rate of informed traders but that this is more than offset by the high quantity of uninformed traders.  Low liquidity stock, by contrast, have fewer information events but informed traders have a much larger effect on prices.

Informed speculation is also used as the theoretical justification for the tendency of Rational Expectations Equilibrium (REE) to prevail in the long-run.  Those economic agents able to determine the fundamental value or discern the underlying economic model will be able to speculate or sell forecasts that will tend to drive prices towards the equilibrium \citet{muth1961Rational}.  This tends to leave uninformed speculation as a pure noise that can be characterised as white-noise random variable. While this construction may be justified for the analysis of microstructure and market efficiency, it is an over-simplification that is inappropriate when seeking more understanding of speculation itself.  Institutional and psychological explanations for noise-trading frequently suggest that there are endogenous non-random elements to speculative activity.

However, a large proportion of uninformed traders in the market can undermine this process.  \citet{Delong1990noise} and \citet{shleifer1997limits} have presented models where \emph{noise-trader risk} can prevent the arbitrate of informed speculators from driving prices back towards the fundamental value.  The risk that noise-traders will drive prices even further away from equilibrium before the convergence can limit the activity of informed speculators when they are risk averse.\footnote{This three-period, overlapping generation model with informed and uninformed traders has a price equation \begin{equation}
p_t = 1 + \frac{\mu(\rho_t - \rho^*)}{1 + r} + \frac{ \mu \rho^*}{r} - \frac{2 \gamma \mu^2 \sigma_{\rho}^2}{r(1 + r^2)}.
\label{eq:NP2}
\end{equation} 
 where $p_t$ is the price; $\mu$ is the share of uninformed traders; $\rho$ is the price mis-perception of the uninformed traders; $\gamma$ is the level of risk aversion; $\sigma^2_{p,t+1}$ is the variance of the misperception.}

@@

The Friedman-effect is the activity of informed speculators.  They take advantage of the space that has been created by the price pressure of the uninformed traders to profit from this mis-pricing.  Uniformed traders tend to hold more when their opinions are strong.  This is the noise-trader risk that can prevent informed traders from fulfilled their arbitrage role. If uninformed traders are very prominent or have strong opinions, prices should show the greatest divergence from fundamental value and the risk of a reversal should be at its greatest.

\subsection{Empirical work}
Empirical assessment of speculation has been limited by the scarcity of data.  It is not very easy to distinguish between speculators and other types of investors.  It is even harder to distinguish between the informed and uninformed.  One approach has been to assume that noise-traders utilise simple investment strategies and to use tests of these strategies as a means of testing speculation.  Common strategies that have been used are momentum (ref), contrarian (ref) and carry (ref).   It is also possible to assume that certain investors usually have more information than others.  For example, hedge funds, investment banks and other professionals can be assumed to be informed while retail or day traders may be uninformed.

@@

However, identifying large orders and making an assessment of the level of informed trading based on that is much harder to achieve in an over-the-counter market like foreign exchange. While electronic order books have become more widely used in recent years, much of the activity still takes place through bilateral agreements.  Information about the nature of transactions including size and origin of orders is not widely available\footnote{\citet{Lyons1995Microstructure} and \citet{Evans2002Order} have used the initiation of orders as an explanatory variable in an equation to explain the evolution of major exchange rates.  They find that $\$$ 1 billion of net US dollar purchase moves the Deutsche mark price of the US unit by 0.5 percent. They argue that the orders crystallise a range of information that is used to value currencies.}    \citet{LeeandReady} seek to use price action to infer the nature of the order that has been placed into the market.  Their tick test has four classifications: the up-tick, the down-tick, the zero-up-tick and the zero-down-tick. A trade is an up-tick if the price is higher than the previous trade.  If the price is the same as the previous trade, if the previous trade was classified as an up-tick, this trade is a zero-up-tick.  
\section{Methodology}
The aim of this study is to assess whether speculation in the foreign exchange market is informed or uninformed. Speculation must be identified and then extreme speculation will then be compared with what would be expected if it were informed or uninformed.  If informed and part of the price-discovery process, extreme speculation would be a function of perceived divergence from equilibrium or new information.  The following price performance should be a random walk.  If speculation is uninformed, extremes should cause a divergence from fundamental value and a price reversal should be anticipated.

@@

\section{Speculation and foreign exchange returns}
This paper has sought to measure speculation and to use this measure to discover more about the relationship between speculation, information and asset prices.  
Whether measured as intensity of speculative sentiment or as the weight of speculator action, it is clear that extreme speculation does not provide information about future returns.  This means that speculation is more likely to be informed than uninformed.  If it were uninformed it would be much more likely that these extremes would be follow by reversals as informed market participants took advantage of the space created by this uninformed speculative activity.

@@

The nature speculation is central to a number of contemporary policy questions.  Amongst these are the design and regulation of financial markets, the surge in commodity prices and the limits put on the activities of financial institutions. The debate about a tax on financial transactions, initiated by \citet{TobinTax} and now called the \emph{the Tobin tax}, has been intended to reduce speculation. The argument for a tax on financial transactions depends on the idea that speculators will drive the price away from its fundamental value. However, if speculation is part of the process of price discovery, reducing its activity may incur costs that offset some of the benefits that are expected.

The reduction in speculation in the US government bond market that has been seen since the introduction of new costs and restrictions under the array of ???? regulations has been seen by some to reduce liquidity and increase volatility, rising risk and imposing additional costs for final investors.
